---
title: "Coding Assignment 03"
date: "`r Sys.Date()`"
output: html_document
text.align: justify
---

----

### Type your student name and ID

Name and ID: 
Teresa Surlis 702557904
---

#### Task 1: Download the Admission dataset and set the work directory:

```{r}
# Make sure to set the work directory where you saved the dataset
```

----

#### Task 2: Download and load the required packages:

```{r}
# your code goes here
library(ggplot2) #load ggplot2
library(pastecs) #load pastecs
library(psych) #load psych
library(readr) #load readr
library(naniar) #load naniar
library(mice) #load mice
```

----

#### Task 3: Load, view and return the structure of the dataset.

```{r}
# your code goes here
Admission<-read.csv("Admission.csv") #load Admission.csv and assign it to a variable called Admission
View(Admission) #view Admission dataset
str(Admission) #return structure of Admission dataset
```

----

#### Task 4: Stroing categorical variables as factors in the dataset

```{r}
# your code goes here
Admission$Major<-as.factor(Admission$Major) #store Major as a factor
Admission$School_GPA<-as.factor(Admission$School_GPA) #store School_GPA as a factor
Admission$Admitted<-as.factor(Admission$Admitted) #store Admitted as a factor
```

----

#### Task 5: Return Summary Statistics of the Admission Dataset:

```{r}
# your code goes here
summary(Admission) #return summary statistics of Admission dataset
```

----

#### Task 6: Summary statistics using the pastecs package.

```{r}
# your code goes here
library(pastecs) #load pastecs
options(scipen=999)
stat.desc(Admission) #return summary statistics of Admission dataset using pastecs package
```

----

#### Task 7: Using the describe function of the psych package to get the Summary statistics for all variables.

```{r}
# your code goes here
library(psych) #load psych
describe(Admission) #return summary statistics of Admission dataset
```

----

#### Task 8: Using the describeBy function to get the Summary statistics for all variables by Major.

```{r}
# your code goes here
library(psych) #load psych
describeBy(Admission~Major) #return summary statistics of Admission dataset by variable Major
```

----

#### Task 9: Using the describeBy function to get the Summary statistics for all variables by Admitted

```{r}
# your code goes here
library(psych) #load psych
describeBy(Admission~Admitted) #return summary statistics of Admission dataset by variable Admitted
```


#### Task 10: Download the Students dataset and set the work directory:

```{r}
# Make sure to set the work directory where you saved the Students dataset
```

----

#### Task 11: Load, view and return the structure of the Students dataset.

```{r}
# your code goes here
Students<-read.csv("Students.csv") #load Students.csv and assign to variable called Students
View(Students) #view Students
str(Students) #return structure of Students
```

----

#### Task 12: Exploring the dataset for missing values using the naniar package.

```{r}
# your code goes here
library(naniar) #load naniar
n_miss(Students) #return number of missing values
n_complete(Students) #return the number of complete values
pct_complete(Students) #return the percentage of complete values
pct_miss(Students) #return percentage of missing values
pct_miss_case(Students) #return percentage of rows with missing values
pct_complete_case(Students) #return percentage of rows with no missing values
gg_miss_var(Students,show_pct=TRUE) #return percentage of missing values
vis_miss(Students) #return heat-map of missing variable
```

----

#### Task 13: Data Imputation.

```{r}
# your code goes here
library(mice)
imputed_dataset=mice(Students,m=5,method=c("","rf","rf","pmm","pmm","pmm"),maxit=5) #impute missing values using mice method
mean(Students$GRE_Score, na.rm=TRUE)
imputed_dataset$imp$GRE_Score
final_imputed_ds=complete(imputed_dataset,2)
```

----

#### Task 14: Viewing the clean Imputed Dataset.

```{r}
# your code goes here
View(final_imputed_ds) #view the imputed dataset
```
